---
title: "Lab1"
author: "Jack Sutton"
date: "2024-09-16"
output: "github_document"
---

# Load Packages
```{r}

library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggstatsplot)
library(psych)
library(bruceR)
library(ggsci)
library(datasauRus)

```

# First look of descriptive statistics 
```{r}

datasaurus_dozen %>% 
  group_by(dataset) %>%
  dplyr::summarize(mean_x    = mean(x),
      mean_y    = mean(y),
      std_dev_x = sd(x),
      std_dev_y = sd(y),
      corr_x_y  = cor(x, y)
    )


```

# Introduce GGplot
```{r}

ggplot(datasaurus_dozen, aes(x = x, y = y, colour = dataset))+
    geom_point() + facet_wrap(~dataset)

dino<- datasaurus_dozen %>%
  filter (dataset == "dino")

ggplot(dino, aes(x = x, y = y))+
    geom_point(color = "#FF00FF")+theme_void() + labs(title = "Hi, I'm a Dino!") + theme(plot.title=element_text(hjust=0.5, face="bold", size=20, color = "pink"))


```

# Q1: What is the function of facet wrap? In what situation do you think you will use this function? 

Facet wraps present each category as its own individual graph. We'll use this to separate categories of interest and group them when we want to visualize certain relationships or variables.


# Q2: The means, standard deviations, and correlations are pretty much the same, but the data pattern looks very different for each dataset. What is the implication here? 

It implies that data visualization is important to discern otherwise similar data sets. If we hadn't separated them with facet wrap and visualized them, we might wrongly assume they are similar/same.